The Next Release Problem in Real World

### 2018-12-18 PaperBody.tex

>>>>

\begin{table*}[t]
\caption{EX3 - Recal of each algorithms on four datasets}
\begin{tabular}{@{}crrrrr@{}}
\toprule
\multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}The limited\\ budget\end{tabular}}} & \multicolumn{5}{c}{Algorithms}                                                                                                    \\ \cmidrule(l){2-6} 
\multicolumn{1}{c}{}                                                                              & \multicolumn{1}{c}{SA} & \multicolumn{1}{c}{GA} & \multicolumn{1}{c}{NSGA-II} & \multicolumn{1}{c}{AHP} & \multicolumn{1}{c}{ILP} \\ \midrule
ECLIPSE & 0.77300 & 0.81435 & 0.82025 & 0.82700 & 0.82363\\
FIREFOX-I & 0.82973 & 0.00000 & 0.85876 & 0.86721 & 0.87302\\
FIREFOX-II & 0.56917 & 0.00000 & 0.60507 & 0.61536 & 0.79725\\
FIREFOX-III & 20906.31785& \textbf{20934.94744}& 20559.69749& 20656.69427& 20873.08535\\\bottomrule
\end{tabular}
\label{table:Recall}
\end{table*}
